Distributional Trees and Forests

### 2017-09-26 pkg/disttree/inst/draft/draft.Rnw
added handling of NAs in averaging over the results within the cross-validation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1591 255f4249-2263-4417-b1ea-8498779e27a7

<<echo=FALSE, results=hide>>=
if(file.exists("simres.rda")){
  load("simres.rda")
} else {
  #source("~/svn/partykit/pkg/disttree/inst/draft/.R")
  source("gensim.R")
  simres <- gensim(seedconst = 7, nrep = 40, ntree = 100,
                   nsteps = 9, stepsize = 1, kappa.start = 1,
                   formula = y~x1+x2+x3+x4+x5+x6+x7+x8+x9+x10, 
                   nobs = 400, testnobs = 200L,
                   tree_minsplit = 14, tree_mincrit = 0.95,
                   forest_minsplit = 7, forest_mincrit = 0, 
                   type.tree = "ctree",
                   censNO = TRUE,
                   fix.mu = FALSE,
                   fix.sigma = FALSE,
                   mu.sigma.interaction = FALSE,
                   gamboost_cvr = FALSE,
                   eval_disttree = TRUE,
                   eval_distforest = TRUE,
                   eval_gamlss = TRUE,
                   eval_bamlss = TRUE,
                   eval_gamboostLSS = TRUE,
                   eval_randomForest = TRUE,
                   eval_cforest = TRUE,
                   mubase = 0)
  save(simres, file = "simres.rda")
}
@

@@

for(i in 1:length(rainres)){
  rain_rmse[i,] <- colMeans(rainres[[i]]$rmse)
  rain_ll[i,] <- colMeans(rainres[[i]]$ll)
  rain_crps[i,] <- colMeans(rainres[[i]]$crps)
}

>>>>

<<echo=FALSE, results=hide>>=
if(file.exists("simres.rda")){
  load("simres.rda")
} else {
  #source("~/svn/partykit/pkg/disttree/inst/draft/.R")
  source("gensim.R")
simres <- gensim(seedconst = 7423, nrep = 10, ntree = 100,
                 nsteps = 4, stepsize = 3, kappa.start = 1,
                 formula = y~x1+x2+x3+x4+x5+x6+x7+x8+x9+x10, 
                 nobs = 700, testnobs = 200L,
                 tree_minsplit = 25, tree_minbucket = 10, tree_mincrit = 0.95,
                 forest_minsplit = 25, forest_minbucket = 10, forest_mincrit = 0, 
                 type.tree = "ctree",
                 censNO = TRUE,
                 fix.mu = FALSE,
                 fix.sigma = FALSE,
                 mu.sigma.interaction = FALSE,
                 gamboost_cvr = FALSE,
                 eval_disttree = TRUE,
                 eval_distforest = TRUE,
                 eval_gamlss = TRUE,
                 eval_bamlss = FALSE,
                 eval_gamboostLSS = TRUE,
                 eval_randomForest = TRUE,
                 eval_cforest = TRUE,
                 mubase = 0)

  save(simres, file = "simres.rda")
}
@

@@

for(i in 1:length(rainres)){
  rain_rmse[i,] <- colMeans(rainres[[i]]$rmse, na.rm = TRUE)
  rain_ll[i,] <- colMeans(rainres[[i]]$ll, na.rm = TRUE)
  rain_crps[i,] <- colMeans(rainres[[i]]$crps, na.rm = TRUE)
}
